---
title: "Penguins EDA"
format:
  html:
    code-fold: true
---

## Penguin Size and Mass by Sex and Species

```{r warning=FALSE, message=FALSE}
library(palmerpenguins)
library(dplyr)
library(ggplot2)
library(DBI)
library(duckdb)
library(dbplyr)
df <- palmerpenguins::penguins
```

```{r warning=FALSE, message=FALSE}
con <- DBI::dbConnect(
  duckdb::duckdb(), 
  dbdir = "my-db.duckdb"
  )
df <- dplyr::tbl(con, "penguins")
```

## Distribution of Flipper Length

```{r warning=FALSE, message=FALSE}
df %>%
ggplot(aes(x = flipper_length_mm)) +
  geom_histogram(binwidth = 5, fill = "darkblue", color = "darkorange") +
  ggtitle("Distribution of Flipper Length") +
  xlab("Flipper Length (mm)") +
  ylab("Count")
```

## Distribution and Bill length

```{r warning=FALSE, message=FALSE}
df %>%
ggplot(aes(x = bill_length_mm)) +
  geom_histogram(binwidth = 5, fill = "darkblue", color = "darkorange") +
  ggtitle("Distribution of Flipper Length") +
  xlab("Flipper Length (mm)") +
  ylab("Count")
```

## Penguin Bill Length vs Mass by Species

```{r warning=FALSE, message=FALSE}
df %>%
  ggplot(aes(x = bill_length_mm, y = body_mass_g, color = species)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = "Bill Length (mm)", 
       y = "Body Mass (g)", 
       title = "Relationship Between Bill Length and Body Mass")
```

```{r message = FALSE, warning = FALSE}
df %>%
ggplot(aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point() +
  labs(
    title = "Bill Length vs Flipper Length",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)"
  )
```

```{r message = FALSE, warning = FALSE}
df %>%
  ggplot(aes(x = bill_length_mm, y = body_mass_g, color = species)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = "Bill Length (mm)", 
       y = "Body Mass (g)", 
       title = "Relationship Between Bill Length and Body Mass",
       color = "Species")
```

![](data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAaCAYAAADFTB7LAAAAcElEQVR4Xu3OwQmAQAxE0bClWYCW5N06tM6V2YPg5CjoF/JhLoHAi6iqn9eOefUbqrYvHY0cQDLyAlKRNyARmYA0ZMLRkAlGQyaU72tkAtlim7r/vJqDUDjlKBROOQyFU2icQuMUGqfQuBEaV1XPOwEx96nYACK8+wAAAABJRU5ErkJggg== "Run Current Chunk"){width="40"}
